\textbf{SPECFEM3D}\\ \textbf{User Manual}

### 2011-04-10 doc/USER_MANUAL/manual_SPECFEM3D.tex
added references to Patera 1984, Seriani et al., Faccioli et al., and also to GeoElse.

@@

The next release of the code will include support for GPU graphics card acceleration \citep{KoMiEr09,KoErGoMi10,MiKo10,Kom11}
as well as Convolutional or Auxiliary Differential Equation Perfectly Matched absorbing Layers (C-PML or ADE-PML) \citep{KoMa07,MaKoEz08,MaKoGe08,MaKo09,MaKoGeBr10}.
It will also use the PT-SCOTCH parallel library for mesh partitioning.

>>>>

The SEM was originally developed in computational fluid dynamics \citep{Pat84,MaPa89}
and has been successfully adapted to address problems in seismic wave propagation.
Early seismic wave propagation applications of the SEM, utilizing Legendre basis functions and a
perfectly diagonal mass matrix, include \cite{CoJoTo93}, \cite{Kom97},
\cite{FaMaPaQu97}, \cite{CaGa97}, \cite{KoVi98} and \cite{KoTr99},
whereas applications involving Chebyshev basis functions and a nondiagonal mass matrix
include \cite{SePr94}, \cite{PrCaSe94} and \cite{SePrPr95}.\\

@@

The next release of the code will include support for GPU graphics card acceleration \citep{KoMiEr09,KoErGoMi10,MiKo10,Kom11}
as well as Convolutional or Auxiliary Differential Equation Perfectly Matched absorbing Layers (C-PML or ADE-PML) \citep{KoMa07,MaKoEz08,MaKoGe08,MaKo09,MaKoGeBr10}.
It will also use the PT-SCOTCH parallel library for mesh partitioning.\\

SPECFEM3D includes coupled fluid-solid domains and
adjoint capabilities, which enables one to address seismological inverse problems, but for linear rheologies so far.
To accommodate visco-plastic or non-linear rheologies, the reader can refer to 
the \href{http://geoelse.stru.polimi.it/}{GeoELSE} software package \citep{CaGa97,StPaIg09,ChMoTsBaKrKaStKr10}.
